GVN-Hoist: Hoisting Computations from Branches

### 2016-08-22 hoist.tex
outlier

While benchmarking llvm-testsuite we see both increase as well as decrease in
the codesizes of the final binaries. Since the pass runs early, it has affect on
many optimizations which rely on number of instructions, lenth of the use-def
chain etc metrics which are affected by code-hoisting. Specially the inliner
where the total inline cost (in llvm) is heavily dependent on the total count of
instructions in the caller and callee. Various code-size metrics are shown in
Table-\ref{tab:code-size}. All but one benchmark varied between -5.32\% and
5.43\%.  In one benchmark FreeBench/distray/distray.test, the codesize increased
by 35.38\%.

>>>>

While benchmarking llvm-testsuite we see both increase as well as decrease in
the codesizes of the final binaries. Since the pass runs early, it has affect on
many optimizations which rely on number of instructions, lenth of the use-def
chain etc metrics which are affected by code-hoisting. Specially the inliner
where the total inline cost (in llvm) is heavily dependent on the total count of
instructions in the caller and callee. Various code-size metrics are shown in
Table-\ref{tab:code-size}. All but one benchmark varied between -5.32\% and
5.43\%.  In one benchmark FreeBench/distray/distray.test, the codesize increased
by 35.38\%. In this benchmark 3 more (15 as compared to 12) functions got
inlined and because of that 10 more (81 vs. 71) vector instructions got
generated, 3 calls got hoisted/sunk as (compared to 0), one loop got unswitched
(compared to 0), 6 high latency machine instructions got hoisted out of loop, 59
(compared ot 30) machine instructions got hoisted out of loop, 70 (compared to
39) machine instructions were sunk.
